\input{../preamble.tex}

%Questions in the application:
% 1) Tell us about a project that involves 3D geometry, calibration, SLAM, or numerical optimisation.
%
% In my current company I have been building a SLAM library in C++ that
% leverages input from LiDAR, IMU, and GPS sensors to localise the robot base in
% the map and create/update the map at the same time. The solutions to the
% problems involved in this system span in all the categories mentioned: sensors
% extrinsics and IMU intrinsics for calibration; lidar points undistortion and
% feature detection for 3D geometry; graph optimisation, ICP alignment, sensor
% fusion, and IMU filtering for numerical optimisation.
%
%
% 2) Which programming languages, frameworks, or tools do you like the most for
% computational geometry/optimisation/visual SLAM-style work, and why ?
%
% I consider a compiled and strongly and statically typed language like C++ or
% Rust an extremely important stepping stone to produce safe, production-ready
% and performant code. I use G2O and GTSAM libraries extensively to write
% optimisation  problems. I greatly enjoy developing the visualisation of the
% systems I build and in C++ I usually create GUIs using ImGui.



\begin{document}

Dear Madam or Sir,
\medskip

I am writing to express my interest in the Senior Software Engineer
- Computer Vision, C++ position at Bolt6.
I am a Senior SLAM Engineer with over 7 years of experience developing
high-performance, production-grade C++ robotics software.

The core values of the company make me excited to join the team.
It strikes me as a great place to work since I am also enthusiastic about most
sports.
\medskip

My technical background aligns closely with the requirements of this role:
\begin{itemize}
\item
    \textbf{Ownership \& maintenance of Computer Vision Products End-to-End}\\
    I have over 7 years of software development experience in C++. I have
    created numerous prototypes, brought them to production, and iteratively
    improved them while maintaining them.
\item
    \textbf{Optimization \& debugging of Real-Time Computer Vision
    applications}\\
    I conducted various investigations to uncover performance issues and elusive
    bugs in production code bases using different profilers and other debugging
    tools like gdb, thread\_sanitizer, Valgrind, and Tracy.
\item
    \textbf{Cross-team collaboration \& culture fit}\\
    I enjoy working in a SAFe (Scaled Agile Framework) environment, planning
    future work carefully, and performing in-depth code reviews.
    In my previous role at Inria I have successfully interfaced with the stakeholders
    involved to obtain the product requirements.
    I am often volunteering suggestions to ameliorate the team's pain points,
    and I find satisfaction in mentoring new engineers, always promoting a
    collaborative team culture.
\item
    \textbf{Proficiency in Computer Vision}\\
    My work in SLAM and state estimation involves complex factor graphs,
    Lie algebra, and covariance propagation.
    I believe that the knowledge gained is transferable to a wide variety of
    computer vision techniques.
    During my career, I have implemented various prototypes starting from the
    white paper.
\item
    \textbf{Solving non-linear least square problems}\\
    Working in SLAM and state estimation, I usually have to model the problem as
    an LS problem. The most recent example is while implementing an improved IMU
    filtering.
\item
    \textbf{Experience in UI development (ImGui)}\\
    I have used the ImGui library extensively, both in Inria and in Kudan,
    developing GUIs and development tools to visualize the system state.
\end{itemize}

\medskip
I consistently prioritize clear software architectures alongside performant implementations.
\smallskip

I am eager to bring my expertise in high-performance software engineering to
Bolt6.
Thank you for your time and consideration.

\smallskip

Yours faithfully,

\medskip

Edoardo Ghini
\end{document}
