\input{../preamble.tex}
\begin{document}

Dear Madam or Sir,
\medskip

I am writing to express my enthusiastic interest in the Autonomy Engineer
(Lidar Perception) role at Dexory.
I am a Senior SLAM Engineer with over 7 years of experience developing
high-performance, production-grade C++ robotics software.

I am impressed by the trajectory of the company, from its inception to this day.
It strikes me as a great place to work.
I would be happy to contribute to the new wave of progress in logistics
automation. 
\medskip

My technical background aligns closely with the requirements of the role:
\begin{itemize}
  \item
    \textbf{Solid understanding of LiDAR-based SLAM algorithms} \\
    At Kudan, I have been maintaining and improving a C++ Lidar SLAM library
    that has been deployed in a production environment.
    Also, during my master's thesis, I re-implemented a 3D Lidar SLAM
    following the white paper of Loam.
  \item
    \textbf{Experience with pose graph optimization, scan matching, and
    sensor fusion} \\
    I have built SLAM back-ends to perform pose graph optimization, leveraging
    libraries like G2O and GTSAM.
    I have created scan matching modules that leverage ICP for convergence.
    I have also contributed to the creation of a sensor fusion module that
    borrows the theoretical backbone from the state estimation book from
    Prof. Timothy Barfoot based on Gaussian Processes.
  \item
    \textbf{ Understanding of state estimation frameworks} \\
    I maintained an error state Kalman filter module for IMU filtering, and
    recently I have re-implemented a white paper that showcases an evolution of
    this approach ( ESKF on manifolds).
    I have a strong understanding of the Lie algebra concepts necessary to
    estimate the uncertainty of the estimated state.
  \item
    \textbf{Experience integrating 3D and 2D LiDARs \& Knowledge of calibration}
    \\
    I have worked with different types of LiDARs and their integration with
    external sensors like IMUs, GPSs, and wheel odometry.
  \item
    \textbf{ Solid experience with ROS 2, C++, and Python} \\
    I have worked with C++ for 7+ years and used Python alongside it as a
    supporting scripting language.
    I have developed ROS nodes during my experience working at Inria and, in
    Kudan, I use ROS2 as a wrapper around the SLAM library.
  \item
    \textbf{Familiarity with Linux, Git, CI/CD, and containerisation} \\
    I have always worked on Linux-based platforms, have a deep understanding of
    version control systems (e.g. Git), and was exposed to continuous integration
    through either Jenkins or GitHub actions. I am a passionate user of Docker and
    prefer to deploy and develop in sandboxed (containerised) environments.
\end{itemize}

I am eager to bring my expertise in LiDAR-based SLAM to Dexory.
Thank you for your time and consideration.

\smallskip

Yours faithfully,

\medskip

Edoardo Ghini
\end{document}
