\input{../preamble.tex}
\begin{document}

Dear Madam or Sir,
\medskip

I am writing to express my enthusiastic interest in the Senior Rust Software Engineer
position at Fractile.
I am a Senior SLAM Engineer with over 7 years of experience developing
high-performance, production-grade C++ robotics software.

I am impressed by the potential of the company.
It strikes me as a great place to work.
I would be proud to contribute to the company mission to scale up the
hardware inference capabilities through the Compute-In-Memory paradigm.
\medskip

My technical background aligns closely with the requirements of this role:
\begin{itemize}

 \item
 \textbf{ Strong senior developers in another systems language} \\
    I have over 7 years of professional
    experience in C++ and Python.
    I have developed a deep understanding of how to make software architectures
    scalable and future-proof and of how to face the challenges brought by
    multithreaded systems.
    I have led the design of major software epics,
    focusing on code quality and modern paradigms to maintain a production-grade 3D LiDAR SLAM library.
    I enjoy working in a SAFe (Scaled Agile
    Framework) environment, planning future work carefully, and performing in-depth code reviews.
    I am often volunteering suggestions to ameliorate the team's pain points,
    and I find satisfaction in mentoring new engineers, always promoting a collaborative team culture.

 \item
 \textbf{ Creative problem solving and capability to tackle hard problems \&
  experience moving large amounts of data around in real-time at low latency} \\
  My work in SLAM and state estimation involves complex factor graphs, Lie
  algebra, covariance propagation, real time requirements, processing extremely
  dense sensor data, and implementing state-of-the-art algorithms from white
  papers.
  I believe that the knowledge gained is transferable to designing and building
  a full AI inference software stack.

\end{itemize}

\medskip

My academic background in artificial intelligence and robotics from La Sapienza
provided me with a strong theoretical understanding of the AI/ML landscape.
I have consistently prioritized clear software architectures alongside performant implementations.
I committed to Rust three years ago, learning and experimenting with it in
my spare time. It would be extremely fulfilling to use Rust professionally.
\smallskip

The Rust projects that I developed are visible on my GitHub:
https://github.com/dinies.
Those projects are named \textbf{hexgame\_rs}, \textbf{sigma\_learning\_rs}, and
\textbf{experiments\_rs}.

\smallskip

I am eager to bring my expertise in high-performance software engineering to
Fractile.
Thank you for your time and consideration.

\smallskip

Yours faithfully,

\medskip

Edoardo Ghini
\end{document}
