\input{../preamble.tex}
\begin{document}

Dear Madam or Sir,
\medskip

I am writing to express my enthusiastic interest in the Software Engineer - PyTorch
position within the Frameworks team at Graphcore.
I am a Senior SLAM Engineer with over 7 years of experience developing
high-performance, production-grade C++ robotics software.

I am impressed by the trajectory of the company, from its inception to this day.
It strikes me as a great place to work.
I agree completely with Graphcore's purpose: "democratized intelligence for
everyone".
\medskip

My technical background aligns closely with the requirements of the PyTorch team:
\begin{itemize}
\item
    Performant C++ \& Python Development: I have over 7 years of professional
    experience in C++ and Python.
    I have developed a deep understanding of how to make software architectures
    scalable and future-proof, and of how to face the challenges brought by
    multithreaded systems.
    I have led the design of major software epics,
    focusing on code quality and modern paradigms to maintain a production-grade 3D LiDAR SLAM library.
\item
    Computationally Intensive Engineering: My work in SLAM and state estimation involves complex
    factor graphs, Lie algebra, and covariance propagation.
    I believe that the knowledge gained is transferable to developing machine
    learning accelerators.
\item
    Agile Leadership \& Collaboration: I enjoy working in a SAFe (Scaled Agile
    Framework) environment, planning future work carefully, and performing in-depth code reviews.
    I am often volunteering suggestions to ameliorate the team's pain points,
    and I find satisfaction in mentoring new engineers, always promoting a collaborative team culture.
\item
    Systems \& Infrastructure: I have extensive experience with Docker and value
    extremely highly the contribution to code maintainability brought by stable CI/CD pipelines.
\end{itemize}

\medskip

My academic background in Artificial Intelligence and Robotics from La Sapienza
provided me with a strong theoretical understanding of the AI/ML landscape.
I have consistently prioritized clear software architectures alongside performant implementations.
Two of the most relevant experiences I gained during that time come from developing a 3D LIDAR SLAM
system from scratch and from experimenting with spiking neural networks in
TensorFlow.
\smallskip

I am eager to bring my expertise in high-performance software engineering to Graphcore.
Thank you for your time and consideration.

\smallskip

Yours faithfully,

\medskip

Edoardo Ghini
\end{document}
