\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{xcolor}
\definecolor{red-milano}{rgb}{0.6,0.04,0}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true, % Whether to color the text of links
	urlcolor=red-milano, % Color for \url and \href links
	linkcolor=red-milano, % Color for \nameref links
}
\usepackage{lmodern} % simple font

\usepackage[margin=0.5cm]{geometry} % Sets all margins


\usepackage{sectsty} % to change color of sections
\chapterfont{\color{red-milano}}
\sectionfont{\color{red-milano}}

\setlength{\parindent}{0pt} % remove indentation after new lines

\pagenumbering{gobble} % no page numbers
\usepackage[none]{hyphenat} % disable hypenation
\sloppy % prevent word-breaking
\raggedright % force left alignment
\frenchspacing % prevent elimination of spaces after punctuation

\usepackage{enumitem} % keep bullet points ATS friendly
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt}

\usepackage{microtype}
\microtypesetup{
  protrusion=false,
  expansion=false
}
\DisableLigatures{encoding = *, family = *} % disable ligatures

\pdfgentounicode=1 % improve copy pasta behaviour

\usepackage{etoolbox}
\makeatletter
\pretocmd\@outputpage{\hspace{0pt}}{}{} % solve last word and first word stitched together
\makeatother

\pagestyle{empty}


\begin{document}
Dear Madam or Sir,
\medskip

I am a Senior Software Engineer with 5+ years of experience, based in Bristol.
I am applying to the Senior Software Engineer role since the job description and the company mission resonated with my professional experience and values:
\begin{itemize}
\item
I believe in clean software architectural design.
\item
I have been following object oriented design principles throughout my career.
\item
I understand the value that Test Driven Development brings to the table: unparalleled bug prevention translating in better code safety.
\item
Passionate about containerisation with Docker.
\item
Worked in codebases where Jenkins was used for CI/CD pipelines.
\end{itemize}
\medskip

I have had exposure to Java at the beginning of my career and after that I worked with C++ and python.
The statement of Lloyds Banking Group excites me together with the company culture: "finance as force for good".
\bigskip

Yours faithfully,
\medskip

Edoardo

\end{document}
