\documentclass[11pt]{article}
\usepackage[
	a4paper, % Paper size
	top=1.75cm, % Top margin
	bottom=1.75cm, % Bottom margin
	left=3.5cm, % Left margin
	right=3.5cm, % Right margin
	footskip=1cm, % Space from the bottom margin to the baseline of the footer
	headsep=0.5cm, % Space from the top margin to the baseline of the header
	headheight=1cm, % Height of the header
	%showframe % Uncomment to show frames around the margins for debugging purposes
]{geometry}

\usepackage[usenames, svgnames]{xcolor} % Required for defining and using custom colors
\definecolor{headings}{HTML}{701112} % Dark red color for headings
\definecolor{linkcolor}{HTML}{641c1d} % 25% desaturated headings color for links

\usepackage{hyperref} % Required for links
\hypersetup{
	colorlinks=true, % Whether to color the text of links
	urlcolor=linkcolor, % Color for \url and \href links
	linkcolor=linkcolor, % Color for \nameref links
}
\usepackage[ddmmyyyy]{datetime}
\usepackage[english]{babel}
\usepackage{ragged2e}
\usepackage[bottom]{footmisc}

% companies names: Airbus, Volkswagen, Honda, Tesla, Vicon
\newcommand{\company}{Vicon}

\begin{document}
\begin{FlushRight}
\today\\
\bigskip
{\sffamily Mr Edoardo Ghini}\\
\textcolor{headings}{Robotics Engineer}\\
\medskip
Bristol, UK\\
+44 788 303 7470\\
ghiniedoardo@gmail.com
\end{FlushRight}

\begin{FlushLeft}
\input{\company}

Usually, when I am working on a project
 I become extremely passionate and channel a lot of energy into it.
If I had to choose, I would say that my two greatest interests are
 Programming and Robotics Control, actually I believe the former to be a form of art.\\\smallskip
Moreover, since undertaking my Masters, I have greatly enjoyed 
  being able to model the evolution of dynamic systems through programming.
  The topic of my master thesis was \textbf{SLAM}.
  \footnote{ \textit{Position tracking in 3D scenes using high order primitives.}
  \quad links to \href{https://github.com/dinies/3D-Lidar-Odometry-and-Tracking}{code} and 
  \href{https://github.com/dinies/MasterThesis-ArtificialIntelligence-Robotics/blob/master/MaterThesis_Edoardo_Ghini.pdf}
  {thesis}.}
I developed a system for autonomous navigation which performs
 3D LIDAR Odometry and Tracking on high order features extracted from the point cloud.\\\smallskip
Since then I have cultivated even more interest in \textbf{autonomous navigation }
 even when that hasn't been the main focus of my job:
 I was employed in INRIA as a robotics engineer where I developed  a system for teleoperation.
During this experience I learned a lot because I was responsible
 for the design and implementation of the entire pipeline software-side:
\begin{itemize}
  \item  dynamic simulation and control starting from URDF description of robots.
  \item  GUI prototyping using an open-source C++ library.
  \item  containerization and automation of the development environment.
  \item  handling communication between modules with ROS.
\end{itemize}
I've been working at Kudan in Bristol for the past two years.
It's a computer vision company that specializes in SLAM solutions using LiDAR and camera sensors.
My role involves developing new features for the C++ LiDAR SLAM library and
checking out how we could use the latest academic research in our work.
These experiences have helped me become an expert in C++.\\\smallskip
Finally, I want to mention an individual academic project that I completed during my masters:
  A \textbf{convolutional neural-net} built with \textbf{Spiking Neurons} in Python
  using \textbf{Tensorflow}, that resembles the behavior of neurons inside the biological brain.\\
I am seeking a role involving opportunities that would allow me to expand my creativity.
Thus, I would greatly appreciate your review of my resume and outlined credentials.
I believe that I would be a valuable addition to the \company\ team.\\\smallskip
At your convenience, I am available for further discussion. I look forward to your response.\\\bigskip
Sincerely,\\
Edoardo Ghini
\end{FlushLeft}

\end{document}
