\input{../preamble.tex}

\begin{document}

Dear Madam or Sir,
\medskip

I am writing to express my interest in the Senior Digital Twin Software
Engineer position at ReOrbit.
I am a Senior SLAM Engineer with over 7 years of experience developing
high-performance, production-grade C++ robotics software.

The core values of the company make me excited to join the team. Especially the
words "curious", "respect", "accountability", "trust", "flexibility", and
"impact".
It strikes me as a great place to work since I have always considered aerospace
technologies as the coolest field of work.
\medskip

My technical background aligns closely with the requirements of this role:
\begin{itemize}
\item
\textbf{ Strong capability in object-oriented C++}\\
    I have over 7 years of software development experience in C++. I have
    created numerous prototypes, brought them to production, and iteratively
    improved them while maintaining them.
\item
    \textbf{ Strong experience in simulation software development including
    system architecture, code review, CI/CD pipelines, and software testing} \\ 
    I am comfortable at coordinating operations in a software development team:
    I am enthusiast to create architectural designs, committed to performing
    thorough code reviews that foster positive feedback and learning, and an
    advocate of the importance of testing.
    I have experience working in Agile teams following SAFe and conducting
    purposeful planning to foresee critical decision points.
\item
  \textbf{ Experience developing high-fidelity, high-frequency, real-time
  software solutions} \\
   Working in SLAM and robotics control systems I am used to dealing with
   real-time constraints, low failure rate requirements and dense data passing
   through the pipemine (e.g., high-frequency and high-density sensors like
   LiDARs).
\item
 \textbf{ Self-motivated and driven, with a proven ability to develop and analyse
  independent projects} //
    In my previous role at Inria I was responsible for the creation of the
    entire software stack of a teleoperated industrial robot: the control
    module, the GUI, the digital twin simulation, the input peripherals
    module, and the interfacing of all the modules via ROS. 
    I have successfully interfaced with the stakeholders involved to obtain
    the product requirements.
    During my work at Kudan, I have led the implementations of algorithms from
    academic papers in production-grade code (e.g., an IMU ESKF on manifolds)
    and created a GUI for internal use by the LiDAR SLAM team in C++. 
\end{itemize}

\medskip

I am eager to bring my expertise in high-performance software engineering to
ReOrbit.
Thank you for your time and consideration.

\smallskip

Yours faithfully,

\medskip

Edoardo Ghini
\end{document}
