\input{../preamble.tex}

%%% Questions on the application form:
% How would people that know you describe you? This could be from a colleague, friend or family perspective. (Please don't use AI to answer this, not looking for a generic answer)

% They describe me as very curious and a great team player who is always happy to help others.
% They also say that I am very dedicated to perfecting my craft, always refining my tools and adopting the latest tech the industry has to offer.
% And, they describe my attitude as extremely optimistic in all situations.

% What motivates you?

% I feel galvanised when I experience being part of a functional team that collaborates successfully towards a common goal.
% I also find it extremely rewarding to lead the design of features and to build new things with code to see them adopted by other team members or customers.




\begin{document}

Dear Madam or Sir,
\medskip

I am writing to express my enthusiastic interest in the Computer Vision Engineer
position at Scanifly.
I am a Senior SLAM Engineer with over 7 years of experience developing
high-performance, production-grade C++ robotics software.

I would be proud to contribute to the company mission to bring operators safety
while also accelerating the expansion of the renewable energy infrastructure.
\medskip

My technical background aligns closely with the requirements of this role:
\begin{itemize}

 \item
 \textbf{Proficiency in Python and C++} \\
    I have over 7 years of professional experience in C++ and Python and
    familiarity with OpenCV and Tensorflow (wich is transferrable to Pytorch).
    I have developed a deep understanding of how to make software architectures
    scalable and future-proof and of how to face the challenges brought by
    multithreaded systems.
 \item
\textbf{Structure-from-Motion, 3D Reconstruction and Photogrammetry \&
Familiarity with Geospatial Data and Visual-Inertial SLAM} 
  My work in LiDAR SLAM and state estimation involves complex factor graphs, Lie
  algebra, covariance propagation, real time requirements, processing extremely
  dense sensor data, and implementing state-of-the-art algorithms from white
  papers.
  \item
  \textbf{Pointcloud and Mesh Processing}
  I have used extensively pointcloud inspection tools like CloudCompare and
  FoxGlove.
  \item
  Confortable creating and working in containerised systems (Docker).
  \item
  I have worked to a very similar problem in one of my previous roles when I was
  developing the entire software stack ( GUI, dynamics-aware controller,
  digital-twin, and driver for input peripherals) for a teleoperation robot:
  an industrial-grade forklift on rails to be mounted on roofs and teleoperated to
  remove asbestos plaques.

\end{itemize}

\medskip

I am eager to bring my expertise in high-performance software engineering to
Scanifly.
Thank you for your time and consideration.

\smallskip

Yours faithfully,

\medskip

Edoardo Ghini
\end{document}
