\input{../preamble.tex}
\begin{document}

Dear Madam or Sir,
\medskip

I am writing to express my enthusiastic interest in the Advanced Software Engineer
position at Vertical Aerospace.
I am a Senior SLAM Engineer with over 7 years of experience developing
high-performance, production-grade C++ robotics software.

I would be proud to contribute to the company mission to make fully electric
public transport, which is unaffected by congested urban traffic, available to everyone.
I can see how this would have extremely positive reverberations on the
environment.  
For this reason and for its commitment to equality and dedication, Vertical
Aerospace strikes me as a great place to work. 

\medskip

My technical background aligns closely with the requirements of this role:
\begin{itemize}

\item \textbf{ Strong software engineering fundamentals \&
proven experience delivering high-quality software} \\
    I have developed a deep understanding of how to make software architectures
    scalable and future-proof and of how to face the challenges brought by
    multithreaded systems.
    I have led the design of major software epics, focusing on code quality
    and modern paradigms to maintain a production-grade 3D LiDAR SLAM library.

\item \textbf{ Proficiency in one or more backend languages} \\
    I have over 7 years of professional experience in C++ and I have been using
    Python for scripting alongside it.
    I have been learning Rust for the last three years.

\item \textbf{ Experience developing on Linux/macOS, using containers} \\
  I have always worked on Unix platforms and, when possible, I prefer to
  develop into containerized environments.

\item \textbf{ Working knowledge of databases, testing, automation, and CI/CD in
agile teams} \\
    I enjoy working in a SAFe (Scaled Agile Framework) environment, planning
    future work carefully, and performing in-depth code reviews.
    I consider software testing as important as the core development.
    I am used to working in CI/CD environments built with Jenkins or GitHub
    actions.

\item
 \textbf{ Confidence to tackle complex, ambiguous challenges} \\
  My work in SLAM and state estimation involves complex factor graphs, Lie
  algebra, covariance propagation, real-time requirements, processing extremely
  dense sensor data, and implementing state-of-the-art algorithms from white
  papers.
  I believe that the knowledge gained is transferable to this role's
  responsibilities, allowing for efficient cross-team communication and the
  capability to deeply understand problems coming from a wide range of
  theoretical backgrounds.
 \end{itemize}

\medskip

I am eager to bring my expertise in high-performance software engineering to
Vertical Aerospace.
Thank you for your time and consideration.

\smallskip

Yours faithfully,

\medskip

Edoardo Ghini
\end{document}
