\begin{FlushLeft}
Dr. Alexandros Paraschos\\

Volkswagen\\

\vspace{2cm}
Dear Dr. Paraschos,\\

Having an ardent interest for Robotics, I have felt compelled to search a job opportunity in Volkswagen.
  It was very exciting for me to hear that the company aims to \textit{solve fully autonomous driving by the second half of the decade }.
  \footnote{Volkswagen newsroom article "Fully automated driving" found \href{ https://www.volkswagen-newsroom.com/en/fully-automated-driving-3633}{\textbf{here}}}\\\smallskip
Honestly, knowing that I contributed to it when this will occur, would assuredly bring me a great sense of fullfillment.
Usually, when I am working on a project that interests me I become extremely passionate and channel a lot of energy into it.
If I had to choose, I would say that my two greatest interests are Programming and Robotics Control, actually I believe the former to be a form of art.\\\smallskip
Moreover, since the time of the first projects in academy I have enjoyed greatly  to be able to model the evolution of dynamic system through programming.
  The topic of my master thesis was about \textbf{SLAM}.
  \footnote{ \textit{Position tracking in 3D scenes using high order primitives.} \quad links to \href{https://github.com/dinies/3D-Lidar-Odometry-and-Tracking}{code} and  \href{https://github.com/dinies/MasterThesis-ArtificialIntelligence-Robotics/blob/master/MaterThesis_Edoardo_Ghini.pdf}{thesis}.}
I developed a system for autonomous navigation which performs 3D LIDAR Odometry and Tracking on high order features extracted form the pointcloud.\\\smallskip
After that I have maturated even more interest in \textbf{autonomous navigation } even if my job after graduation focused on something else entirely: I was employed in INRIA as a robotics engineer where I developed  a system for teleoperation.
During this experience I learned a lot because I was responsible of the design and implementation of the entire pipeline software-side:
\begin{itemize}
  \item  dynamic simulation and control starting form URDf description of robots.
  \item  GUI prototyping using an open source C++ library.
  \item  containerization and automation of the development environment.
  \item  handling communication between modules with ROS.
\end{itemize}
In both these experiences I have built a strong C++ foundation.\\\smallskip
I am seeking a working opportunity that would allow expressing my creativity.
In particular I am searching for an engineering position in a research and development team.
Thus, I think that Volswagen will be one of the best companies to ask for it.


\bigskip
Sincerely,\\
Edoardo Ghini
\end{FlushLeft}

