\input{../../preamble.tex}

\begin{document}
\begin{center}
 \textbf{\color{red-milano}\huge{Auriga \\ Senior Mapping Engineer}}
\end{center}

% External Recruiter for this role is Daniel Jones
% First round is with CTO Wallizada Mohibullah

\section*{Common interview questions}
\begin{itemize}
\item \textbf{ What do you know about the company?}\\
  Auriga is at the forefront of autonomous fleet navigation and management in
  industrial settings.
  Their products stem in a few different categories:
  - Mapping and localisation: SLAM
  - Operative system - autonomous - enables oversight and operational control
  - Fleet management - task allocation - incident response
  - Simulation - digital twin
  - Equipping Vehicles with the needed sensors
\item \textbf{ Why do you think you are a good fit for our company?}\\
  Because I have several years of experience in LiDAR based SLAM systems that
  have been deployed in real environments.
  I have also developed my understanding of simulation e.g. digital twin,
  teleoperation, control, and coordination of modules while working in France.
  I have an accademic background in control theory, planning, and probabilistic
  approaches for state estimation.
  I have worked on state estimation components and a sensor fusion module in
  Kudan. I have developed a knowledgebase of differential geometry e.g. Lie
  algebra, filtering approaches, spatial sampling, maps architecture, common
  bottle necks and pain points encountered in SLAM.
  Examples of bottle necks:
  - Huge memory requirements for dense maps
  - Difficulty in architecting a shared map with data coming from different
  sensors
  - Enable the map to be updated dynamically: recognise changes, forget old
  parts.

\item \textbf{ Why do you want to work for us?}\\
  I find it very rewarding to work in this field (SLAM), I look forward to
  approaching the related challenges.
  I like the idea of contributing to shape the product I am working on.
  I see great potential for Auriga as it is approaching the challenge of
  enabling autonomous navigation for large vehicles with an extremely complete,
  multi-faceted solution composed of several pieces that work together to offer
  an effective user experience and achieving an high level of safety
  I like to be part of a team of coworkers that share the same vision. I like to
  feel I am making a positive impact on the products and on the progression of
  other team members.
  \end{itemize}






\end{document}
