\input{../../preamble.tex}

\begin{document}
\begin{center}
 \textbf{\color{red-milano}\huge{Sony Play-Station \\ Software Engineer II }}
\end{center}

% Recruiter for the first introductory call is David Gavin

\section*{Common interview questions}
\begin{itemize}
\item \textbf{ What do you know about the company?}\\
  I know that it is an amazing place to work and that it is responsible for all
  the exciting developments happening in the gaming industry.
  It is also a place where the highest quality of the products and tools is
  prioritized to ensure that both game creators and gamers have the best
  experience possible.
\item \textbf{ Why do you think you are a good fit for our company?}\\
  I am someone that likes to deliver high quality work. I find satisfaction in
  being part of a functional team where the contribution is shared and
  coordinated with insightful design.
  My 7+ years of experience in C++ development would allow me bring value to the
  team, together with my positive attitude.
  One of my strengths, in software development, is the understanding of the
  importance of testing: I believe that tests are equally important to the core
  logic, if not more, since they declare the developer expectations and make
  maintainability of a large code base possible.
  I have worked in multiple projects that created tools useful for development:
  GUIs and CLIs. 
\item \textbf{ Why do you want to work for us?}\\
  Becoming part of the PlayStation team would be an amazing achievement for me: I
  have always been enthusiastic about the video games world and I believe that
  PlayStation created and maintained the best software environment and hardware
  components.
  I also would be excited to join such a recognised company that prioritizes an
  inclusive and diverse work environment, sounds like a great place where to
  focus on my career development.

\end{itemize}

\end{document}
